%!TEX root = ../main.tex  
%!TEX options=--shell-escape  

%%%%%%%%%%%%%%%%%%%%%% pref.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample preface
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%

\preface
\index{preface}
%% Please write your preface here
Here come the golden words


%% Please "sign" your preface
\vspace{1cm}
\begin{flushright}\noindent
place(s),\hfill {\it First name  Surname}\\
month year\hfill {\it First name  Surname}\\
\end{flushright}


\section*{Known issues with typesetting this document}
\index{750words}

\subsection*{Author index generation}
The documentclass does not support author indices directly.
The author index is formatted using the listofauthors command.
This command is defined in the Preamble. 
I found this command online.
I tried to add the multicols environment.
The rightmost column overlapped with the header line on the first page of the index.
Hiding this line might solve the problem.

\subsection*{Underscores and the xurl package}
This package cannot handle underscores in URLs.
I obtained a memory error.
The solution was to comment out the xrul package.
The solution was provided by Dr. LainTze Lim of Overleaf.

\subsection*{Do not overuse labels}
Add labels only when you need them.
They will be unreferenced and will trigger many warnings.
In addition, do not use labels in templates that write TeX files unless you write unique labels.
Otherwise, you will get a warning about multiple identical labels.
It is the situation with the month.tex files.
All twelve had an intro label.


RAM may limit 750words to one document per year.


